### 2022-07-20 FALCON_description.tex
fixed

\begin{figure}
\centering
\noindent\includegraphics[width=\textwidth]{./Figures/errors.pdf}
\caption{Velocity and pressure error for the Stokes flow experiment between generated and analytical solution as a function of element size (panel a),
and comparison between smoothed pressure and analytical solution as function of $x$ coordinate for a grid resolution of \num{128x128} elements (panel b).}
\label{fig:errors}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{./Figures/MUMPS.pdf}
\caption{Panel a) Analysis, factorisation, solution and total solve times (panel a) and factorisation memory usage (panel b) as a function of the total number
of degrees of freedom for the Stokes flow experiment.}
\label{fig:MUMPS}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=200px]{./Figures/Zalesak.pdf}
\caption{Position of the Zalesak disk at $t=0$, 0.25, 0.5 and 0.75 (orange, red, blue and green, respectively) for the case with Courant number of 1.}
\label{fig:runge}
\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/zal_marker.pdf}
\caption{Distance from the centre as function of time for values of Courant number of  of 0.25, 0.3, 0.5, 0.75 and 1 (green, orange, blue, black and red,
respectively). R indicates the distance from the centre considering a perfect circle trajectory.}
\label{fig:runge_err}
\end{figure}

\subsection{Conservative Velocity Interpolation (CVI)}\label{sec:CVI}
The CVI correction is checked by means of the Stokes flow experiment by \citet{Donea2003}, as presented in \ref{sec:stokes}. The advection of Lagrangian
markers is performed using either a 2nd-order or a 4th-order Runge-Kutta scheme with CFL=0.5 and an initial random distribution of 25 markers per element.
Fig. \ref{fig:CVI} shows the minimum and maximum values of markers per element throughout the experiment with and without the CVI correction and using
different Runge-Kutta schemes. The introduction of the CVI correction allows the
tests to run for times longer than $t=2000$ without show empty elements, while tests without the CVI correction stop at approximately $t=600$, when at least
one element goes empty. Fig. \ref{fig:CVI_time} shows the different number of markers per element and the markers distribution at $t=600$ obtained without and
with the CVI correction (panels b and c, respectively) in case of a 2nd-order Runge-Kutta scheme. All data can be found at
\url{https://github.com/aleregorda/Benchmarks/tree/main/Advection/CVI}.
\begin{figure}
\centering
\noindent\includegraphics[width=\textwidth]{./Figures/CVI.pdf}
\caption{Maximum and minimum number of markers per element throughout the experiment, with (green and orange lines) or without (purple and blue lines)
the CVI correction and using either a 2nd-order (blue and orange lines) or a 4th-order (purple and green lines) Runge-Kutta scheme.}
\label{fig:CVI}
\end{figure}
\begin{figure}
\centering
\noindent\includegraphics[width=\textwidth]{./Figures/CVI_time.pdf}
\caption{Number of markers per element and markers distribution through time using 2nd.order Runge-Kutta scheme.
Panels a: number of markers per element (panel a1) and distribution of the markers (panel a2) after the first
iteration; panels b and c: comparison between number of markers per element (panels b1 and c1) and markers distribution (panels b2 and c2) without and with
the CVI correction at $t=600$; panels d: number of markers per element (panel d1) and markers distribution (panel d2) in case of CVI correction at $t=2000$.}
\label{fig:CVI_time}
\end{figure}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{./Figures/Poiseuille.pdf}
\caption{Velocity field (panel a), pressure (panel b) and divergence velocity of a Poiseuille flow in case of the classic penalty method (no iterations) and
after one Uzawa iteration (panel c and d, respectively).}
\label{fig:poiseuille}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{./Figures/Analytical.pdf}
\caption{Velocity (panel a) and pressure (panel b) field predicted by the model for a Poiseuille flow with respect with their analytical solutions. The
velocity field is plotted as function of the vertical coordinate in $L_x/2$ and the pressure is plotted as function of the x coordinate in $L_y/2$.}
\label{fig:poi_plot}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/vrms_NS.pdf}
\caption{$v_{\textrm{rms}}$ as function of element size for the instantaneous 2D sphere experiment in case of no slip boundary conditions and with different average
schemes for the viscosity. Results are compared with results obtained by other numerical codes.}
\label{fig:inst_sphere}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/RT.pdf}
\caption{$v_{\textrm{rms}}$ of the Rayleigh-Taylor experiment as function of time for different resolution of the grid.}
\label{fig:RT}
\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=300px]{./Figures/Rayleigh.pdf}
\caption{Evolution of the Rayleigh-Taylor experiment for a grid of \num{256x256} elements at $t=0, 500, 1000$ and $2000$ (panels a, b, c and d, respectively).}
\label{fig:rayleigh}
\end{figure}

@@

\begin{figure}
\noindent\includegraphics[width=300px]{./Figures/Block.pdf}
\centering
\caption{Density evolution of the falling block experiment at $t=$ \SI{0}{\mega\year} (panel a) and $t=$ \SI{20}{\mega\year} for different viscosities of the
block (panels b-f).}
\label{fig:block}
\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Falling.pdf}
\caption{Initial velocity relative to the density contrast at the centre of the falling block as function of the viscosity contrast between the block and the
surrounding fluid.}
\label{fig:falling}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/vrms_arithm.pdf}
\caption{$v_{\textrm{rms}}$ for different grid resolutions as function of time for the 2D time-dependent Stokes sphere experiment in case of an arithmetic average.
Results are compared with results obtained by ASPECT.}
\label{fig:inst_spherefs}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Kaus_random.pdf}
\caption{Evolution of the y coordinate in $x=L_x$ as function of time for different time steps, with and without the stabilisation algorithm.}
\label{fig:stab}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Crameri.pdf}
\caption{Maximum topography as function of time for the Crameri benchmark (coloured lines) in comparison with the analytical solution (black line) and results
obtained with UNDERWORLD (yellow line) and SULEC (blue line).}
\label{fig:crameri}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Subduction.pdf}
\caption{Maximum depth of the slab as function of time for all the simulations of the \citet{Schmeling2008} benchmark, in case of harmonic, geometric and
arithmetic means (red, green and blue lines, respectively) using a sticky air or a true free surface (discontinuous and continuous lines, respectively).
Red, green and blue rectangular areas indicate the range of times from \citet{Schmeling2008} when the slab tip reaches \SI{500}{\km} in case of sticky air,
while the grey rectangular area indicates the range of times from \citet{Schmeling2008} when the slab tip reaches \SI{600}{\km} in case of true free surface.}
\label{fig:subduction}
\end{figure}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{./Figures/Slab.pdf}
\caption{Effective viscosity for the slab detachment benchmark at the beginning of the evolution (panel a) and when necking is complete (panel b).}
\label{fig:slab}
\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Necking.pdf}
\caption{Normalised width of the necking of the slab detachment benchmark as function of normalised time.}
\label{fig:necking}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Indenter.pdf}
\caption{Viscosity (panels a and b), strain rate (panels c and d), velocity (panels e and f) and pressure (panels g and h) fields for rough (left column) and
smooth (right column) punch experiments.}
\label{fig:indenter}
\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Smooth_Rough.pdf}
\caption{Nodal pressure in function of the x coordinate at $y=1$ for rough (green line) and smooth (blue line) punch experiment. Black and red lines indicate
the analytical solution at $x=0.5$ and $x=0.5 \pm w_p$, respectively.}
\label{fig:smooth_p}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Brick_Beam.pdf}
\caption{Shear band angles predicted for the brick experiment for $\phi=0$° (panel a) and for $\phi=20$° in case of compression and extension (panels b and c,
respectively).}
\label{fig:brick_beam}
\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Brick.pdf}
\caption{Shear band angles predicted for the brick experiment in case of compressional and extensional contexts as function of different internal angle of
friction (continuous black line and red dots), compared with theoretical Roscoe, Artur and Coulomb angles (discontinuous black lines). Red lines indicate the
range of angles calculated at different depths.}
\label{fig:brick}
\end{figure}

\begin{figure}
  \centering
  \noindent\includegraphics[width=500px]{./Figures/convergence.pdf}
  \caption{Convergence rates for all tests. Normalised residuals (left column) are compared with velocity residuals (right column) for extensional (first row)
  and compressional (second row) settings.}
  \label{fig:convergence}
  \end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Advection.pdf}
\caption{Temperature profile as function of \textit{x} for the advection stabilisation benchmark. Purple line indicates the initial temperature profile; the
green line indicates the analytical temperature profile after 250 time steps; blue line indicates the temperature profile after 250 time steps in case of the
classic Galerkin method ($\gamma=0$); orange line indicates the temperature profile after 250 time steps in case of the SUPG method ($\gamma=0.045$).}
\label{fig:advection}
\end{figure}

@@

%\begin{figure}
%\centering
%\noindent\includegraphics[width=400px]{./Figures/Energy_Thieulot.pdf}
%\caption{Temperature and shear heating predicted by the model after 1 time step.}
%\label{fig:en_thieulot}
%\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=500px]{./Figures/Analytical_Shear.pdf}
\caption{Velocity (panel a), temperature (panel b) and shear heating (panel c) as function of the \textit{y} coordinate for the simple shear experiment. The
solutions predicted by the model (red lines) are compared with the analytical solutions (dashed blue lines).}
\label{fig:analytical_en}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Energy.pdf}
\caption{Comparison between shear (first column), adiabatic (second column) and total (third column) energy predicted by the code (panels a, b and c) and those
created using example ${Shear\_adiabatic\_heating.m}$ from Exercise 9.4 in \citet{Gerya2010} (panels d, e and f).}
\label{fig:energy}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Convection.pdf}
\caption{$v_{\textrm{rms}}$ (panels a, c and e) and Nu (panels b, d and f) for the mantle convection benchmark as function of time for different grid resolution.
Panels a and b show the results for $Ra=10^4$; Panels c and d show the results for $Ra=10^5$; panels e and f show the results for $Ra=10^6$. Purple lines
indicate the convergence values for the $v_{\textrm{rms}}$ and the Nu from \citet{Blankenbach1989} at the steady state.}
\label{fig:mantle}
\end{figure}

\begin{table}[H]
\caption{Comparison between $v_{\textrm{rms}}$ and Nu predicted by the code for the mantle convection experiment and same values as reported in literature.}
\centering
\small
\begin{tabular}{|>{\centering}m{0.09\textwidth}|>{\centering}m{0.05\textwidth}|>{\centering}m{0.24\textwidth}|>{\centering}m{0.15\textwidth}|
  >{\centering}m{0.1\textwidth} >{\centering}m{0.1\textwidth} >{\centering\arraybackslash}m{0.1\textwidth}|}
\toprule
& & \multirow{2}{*}{\citet{Blankenbach1989}} & \citet{Thieulot2014} & \multicolumn{3}{c|}{FALCON}  \\
 & & & \num{200x200} & \num{32x32} & \num{64x64} & \num{128x128}  \\
\midrule
\multirow{2}{*}{$Ra=10^4$} & $v_{\textrm{rms}}$ & $42.864947 \pm 0.000020$ & 42.867 & 42.83226 & 42.852793 & 42.861394  \\
           & Nu      & $4.884409 \pm 0.000010$  & 4.882  & 4.781297 & 4.857475  & 4.877573   \\
\hline
\multirow{2}{*}{$Ra=10^5$} & $v_{\textrm{rms}}$ & $193.21454 \pm 0.00010$  & 193.255& 193.872643 & 193.377472 & 193.252290  \\
           & Nu      & $10.534095 \pm 0.000010$ & 10.507 & 9.602514 & 10.270735  & 10.465629   \\
\hline
\multirow{2}{*}{$Ra=10^6$} & $v_{\textrm{rms}}$ & $833.98977 \pm 0.00020$  & 834.712& 848.091176 & 837.767911 & 834.945793  \\
           & Nu      & $21.972465 \pm 0.000020$ & 21.695 & 15.999266 & 19.703682  & 21.306939   \\
\bottomrule
\end{tabular}
\label{tab:mantle}
\end{table}

@@

  \resizebox{\textwidth}{!}{

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/vrms_thin.pdf}
\caption{$v_{\textrm{rms}}$ for the thin layer experiment as function of time for different grid resolution. Results are compared with results obtained by
\citet{vanKeken1997} (black lines) and with ASPECT and ELEFANT.}
\label{fig:thin}
\end{figure}

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/vrmszero.pdf}
\caption{$v_{\textrm{rms}}$ at $t=0$ for the thin layer experiment as function of the element size for different aspect ratios of the elements. Results are compared
with results obtained by \citet{vanKeken1997} (black dots in the grey area) and with ASPECT and ELEFANT.}
\label{fig:thin_initial}
\end{figure}

@@

\begin{figure}
\centering
\noindent\includegraphics[width=400px]{./Figures/Hydration.pdf}
\caption{Distribution of bound and free water (left and right columns, respectively) at $t=0.5$ and $t=$ \SI{1.25}{\mega\year} (first and second rows,
respectively) for the sinking hydrated cylinder experiment. Only markers with bound or free water not equal to 0 are plotted.}
\label{fig:quinquis}
\end{figure}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth]{./Figures/Fraction.pdf}
\caption{Isobaric melting curves for 1 GPa (panel a) and 3 GPa (panel b) as function of temperature with different bulk water contents.}
\label{fig:fraction}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{./Figures/Water.pdf}
\caption{Isobaric melting curves for 1.5 GPa as function of bulk water (panel a) and water in the melt (panel b) calculated for different temperatures.}
\label{fig:water}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{./Figures/errors.pdf}
\caption{Velocity and pressure error for the Stokes flow experiment between generated and analytical solution as a function of element size (panel a),
and comparison between smoothed pressure and analytical solution as function of $x$ coordinate for a grid resolution of \num{128x128} elements (panel b).}
\label{fig:errors}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/MUMPS.pdf}
\caption{Panel a) Analysis, factorisation, solution and total solve times (panel a) and factorisation memory usage (panel b) as a function of the total number
of degrees of freedom for the Stokes flow experiment.}
\label{fig:MUMPS}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=200px]{./Figures/Zalesak.pdf}
\caption{Position of the Zalesak disk at $t=0$, 0.25, 0.5 and 0.75 (orange, red, blue and green, respectively) for the case with Courant number of 1.}
\label{fig:runge}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/zal_marker.pdf}
\caption{Distance from the centre as function of time for values of Courant number of  of 0.25, 0.3, 0.5, 0.75 and 1 (green, orange, blue, black and red,
respectively). R indicates the distance from the centre considering a perfect circle trajectory.}
\label{fig:runge_err}
\end{figure}

\subsection{Conservative Velocity Interpolation (CVI)}\label{sec:CVI}
The CVI correction is checked by means of the Stokes flow experiment by \citet{Donea2003}, as presented in \ref{sec:stokes}. The advection of Lagrangian
markers is performed using either a 2nd-order or a 4th-order Runge-Kutta scheme with CFL=0.5 and an initial random distribution of 25 markers per element.
Fig. \ref{fig:CVI} shows the minimum and maximum values of markers per element throughout the experiment with and without the CVI correction and using
different Runge-Kutta schemes. The introduction of the CVI correction allows the
tests to run for times longer than $t=2000$ without show empty elements, while tests without the CVI correction stop at approximately $t=600$, when at least
one element goes empty. Fig. \ref{fig:CVI_time} shows the different number of markers per element and the markers distribution at $t=600$ obtained without and
with the CVI correction (panels b and c, respectively) in case of a 2nd-order Runge-Kutta scheme. All data can be found at
\url{https://github.com/aleregorda/Benchmarks/tree/main/Advection/CVI}.
\begin{figure}
\centering
\includegraphics[width=\linewidth]{./Figures/CVI.pdf}
\caption{Maximum and minimum number of markers per element throughout the experiment, with (green and orange lines) or without (purple and blue lines)
the CVI correction and using either a 2nd-order (blue and orange lines) or a 4th-order (purple and green lines) Runge-Kutta scheme.}
\label{fig:CVI}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{./Figures/CVI_time.pdf}
\caption{Number of markers per element and markers distribution through time using 2nd-order Runge-Kutta scheme.
Panels a: number of markers per element (panel a1) and distribution of the markers (panel a2) after the first
iteration; panels b and c: comparison between number of markers per element (panels b1 and c1) and markers distribution (panels b2 and c2) without and with
the CVI correction at $t=600$; panels d: number of markers per element (panel d1) and markers distribution (panel d2) in case of CVI correction at $t=2000$.}
\label{fig:CVI_time}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/Poiseuille.pdf}
\caption{Velocity field (panel a), pressure (panel b) and divergence velocity of a Poiseuille flow in case of the classic penalty method (no iterations) and
after one Uzawa iteration (panel c and d, respectively).}
\label{fig:poiseuille}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/Analytical.pdf}
\caption{Velocity (panel a) and pressure (panel b) field predicted by the model for a Poiseuille flow with respect with their analytical solutions. The
velocity field is plotted as function of the vertical coordinate in $L_x/2$ and the pressure is plotted as function of the x coordinate in $L_y/2$.}
\label{fig:poi_plot}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/vrms_NS.pdf}
\caption{$v_{\textrm{rms}}$ as function of element size for the instantaneous 2D sphere experiment in case of no slip boundary conditions and with different average
schemes for the viscosity. Results are compared with results obtained by other numerical codes.}
\label{fig:inst_sphere}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/RT.pdf}
\caption{$v_{\textrm{rms}}$ of the Rayleigh-Taylor experiment as function of time for different resolution of the grid.}
\label{fig:RT}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=300px]{./Figures/Rayleigh.pdf}
\caption{Evolution of the Rayleigh-Taylor experiment for a grid of \num{256x256} elements at $t=0, 500, 1000$ and $2000$ (panels a, b, c and d, respectively).}
\label{fig:rayleigh}
\end{figure}

@@

\begin{figure}
\includegraphics[width=300px]{./Figures/Block.pdf}
\centering
\caption{Density evolution of the falling block experiment at $t=$ \SI{0}{\mega\year} (panel a) and $t=$ \SI{20}{\mega\year} for different viscosities of the
block (panels b-f).}
\label{fig:block}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Falling.pdf}
\caption{Initial velocity relative to the density contrast at the centre of the falling block as function of the viscosity contrast between the block and the
surrounding fluid.}
\label{fig:falling}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/vrms_arithm.pdf}
\caption{$v_{\textrm{rms}}$ for different grid resolutions as function of time for the 2D time-dependent Stokes sphere experiment in case of an arithmetic average.
Results are compared with results obtained by ASPECT.}
\label{fig:inst_spherefs}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Kaus_random.pdf}
\caption{Evolution of the y coordinate in $x=L_x$ as function of time for different time steps, with and without the stabilisation algorithm.}
\label{fig:stab}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Crameri.pdf}
\caption{Maximum topography as function of time for the Crameri benchmark (coloured lines) in comparison with the analytical solution (black line) and results
obtained with UNDERWORLD (yellow line) and SULEC (blue line).}
\label{fig:crameri}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Subduction.pdf}
\caption{Maximum depth of the slab as function of time for all the simulations of the \citet{Schmeling2008} benchmark, in case of harmonic, geometric and
arithmetic means (red, green and blue lines, respectively) using a sticky air or a true free surface (discontinuous and continuous lines, respectively).
Red, green and blue rectangular areas indicate the range of times from \citet{Schmeling2008} when the slab tip reaches \SI{500}{\km} in case of sticky air,
while the grey rectangular area indicates the range of times from \citet{Schmeling2008} when the slab tip reaches \SI{600}{\km} in case of true free surface.}
\label{fig:subduction}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/Slab.pdf}
\caption{Effective viscosity for the slab detachment benchmark at the beginning of the evolution (panel a) and when necking is complete (panel b).}
\label{fig:slab}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Necking.pdf}
\caption{Normalised width of the necking of the slab detachment benchmark as function of normalised time.}
\label{fig:necking}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Indenter.pdf}
\caption{Viscosity (panels a and b), strain rate (panels c and d), velocity (panels e and f) and pressure (panels g and h) fields for rough (left column) and
smooth (right column) punch experiments.}
\label{fig:indenter}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Smooth_Rough.pdf}
\caption{Nodal pressure in function of the x coordinate at $y=1$ for rough (green line) and smooth (blue line) punch experiment. Black and red lines indicate
the analytical solution at $x=0.5$ and $x=0.5 \pm w_p$, respectively.}
\label{fig:smooth_p}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Brick_Beam.pdf}
\caption{Shear band angles predicted for the brick experiment for $\phi=0$° (panel a) and for $\phi=20$° in case of compression and extension (panels b and c,
respectively).}
\label{fig:brick_beam}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Brick.pdf}
\caption{Shear band angles predicted for the brick experiment in case of compressional and extensional contexts as function of different internal angle of
friction (continuous black line and red dots), compared with theoretical Roscoe, Artur and Coulomb angles (discontinuous black lines). Red lines indicate the
range of angles calculated at different depths.}
\label{fig:brick}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=500px]{./Figures/convergence.pdf}
  \caption{Convergence rates for all tests. Normalised residuals (left column) are compared with velocity residuals (right column) for extensional (first row)
  and compressional (second row) settings.}
  \label{fig:convergence}
  \end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Advection.pdf}
\caption{Temperature profile as function of \textit{x} for the advection stabilisation benchmark. Purple line indicates the initial temperature profile; the
green line indicates the analytical temperature profile after 250 time steps; blue line indicates the temperature profile after 250 time steps in case of the
classic Galerkin method ($\gamma=0$); orange line indicates the temperature profile after 250 time steps in case of the SUPG method ($\gamma=0.045$).}
\label{fig:advection}
\end{figure}

@@

%\begin{figure}
%\centering
%\includegraphics[width=400px]{./Figures/Energy_Thieulot.pdf}
%\caption{Temperature and shear heating predicted by the model after 1 time step.}
%\label{fig:en_thieulot}
%\end{figure}

\begin{figure}
\centering
\includegraphics[width=500px]{./Figures/Analytical_Shear.pdf}
\caption{Velocity (panel a), temperature (panel b) and shear heating (panel c) as function of the \textit{y} coordinate for the simple shear experiment. The
solutions predicted by the model (red lines) are compared with the analytical solutions (dashed blue lines).}
\label{fig:analytical_en}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Energy.pdf}
\caption{Comparison between shear (first column), adiabatic (second column) and total (third column) energy predicted by the code (panels a, b and c) and those
created using example ${Shear\_adiabatic\_heating.m}$ from Exercise 9.4 in \citet{Gerya2010} (panels d, e and f).}
\label{fig:energy}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Convection.pdf}
\caption{$v_{\textrm{rms}}$ (panels a, c and e) and Nu (panels b, d and f) for the mantle convection benchmark as function of time for different grid resolution.
Panels a and b show the results for $Ra=10^4$; Panels c and d show the results for $Ra=10^5$; panels e and f show the results for $Ra=10^6$. Purple lines
indicate the convergence values for the $v_{\textrm{rms}}$ and the Nu from \citet{Blankenbach1989} at the steady state.}
\label{fig:mantle}
\end{figure}

\begin{table}[H]
\caption{Comparison between $v_{\textrm{rms}}$ and Nu predicted by the code for the mantle convection experiment and same values as reported in literature.}
\centering
\small
\begin{tabular}{|>{\centering}m{0.09\linewidth}|>{\centering}m{0.05\linewidth}|>{\centering}m{0.24\linewidth}|>{\centering}m{0.15\linewidth}|
  >{\centering}m{0.1\linewidth} >{\centering}m{0.1\linewidth} >{\centering\arraybackslash}m{0.1\linewidth}|}
\toprule
& & \multirow{2}{*}{\citet{Blankenbach1989}} & \citet{Thieulot2014} & \multicolumn{3}{c|}{FALCON}  \\
 & & & \num{200x200} & \num{32x32} & \num{64x64} & \num{128x128}  \\
\midrule
\multirow{2}{*}{$Ra=10^4$} & $v_{\textrm{rms}}$ & $42.864947 \pm 0.000020$ & 42.867 & 42.83226 & 42.852793 & 42.861394  \\
           & Nu      & $4.884409 \pm 0.000010$  & 4.882  & 4.781297 & 4.857475  & 4.877573   \\
\hline
\multirow{2}{*}{$Ra=10^5$} & $v_{\textrm{rms}}$ & $193.21454 \pm 0.00010$  & 193.255& 193.872643 & 193.377472 & 193.252290  \\
           & Nu      & $10.534095 \pm 0.000010$ & 10.507 & 9.602514 & 10.270735  & 10.465629   \\
\hline
\multirow{2}{*}{$Ra=10^6$} & $v_{\textrm{rms}}$ & $833.98977 \pm 0.00020$  & 834.712& 848.091176 & 837.767911 & 834.945793  \\
           & Nu      & $21.972465 \pm 0.000020$ & 21.695 & 15.999266 & 19.703682  & 21.306939   \\
\bottomrule
\end{tabular}
\label{tab:mantle}
\end{table}

@@

  \resizebox{\linewidth}{!}{

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/vrms_thin.pdf}
\caption{$v_{\textrm{rms}}$ for the thin layer experiment as function of time for different grid resolution. Results are compared with results obtained by
\citet{vanKeken1997} (black lines) and with ASPECT and ELEFANT.}
\label{fig:thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/vrmszero.pdf}
\caption{$v_{\textrm{rms}}$ at $t=0$ for the thin layer experiment as function of the element size for different aspect ratios of the elements. Results are compared
with results obtained by \citet{vanKeken1997} (black dots in the grey area) and with ASPECT and ELEFANT.}
\label{fig:thin_initial}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/Hydration.pdf}
\caption{Distribution of bound and free water (left and right columns, respectively) at $t=0.5$ and $t=$ \SI{1.25}{\mega\year} (first and second rows,
respectively) for the sinking hydrated cylinder experiment. Only markers with bound or free water not equal to 0 are plotted.}
\label{fig:quinquis}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/Fraction.pdf}
\caption{Isobaric melting curves for 1 GPa (panel a) and 3 GPa (panel b) as function of temperature with different bulk water contents.}
\label{fig:fraction}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{./Figures/Water.pdf}
\caption{Isobaric melting curves for 1.5 GPa as function of bulk water (panel a) and water in the melt (panel b) calculated for different temperatures.}
\label{fig:water}
\end{figure}
